### 2013-09-18 chi2014/results.tex

We fit the parameters to the data using a Bayesian approach \cite{kruschke_doing_201}, using the STAN modeling software to perform the actual fit \cite{stan-software:2013}. In modeling the parameters, we use uninformative priors. The resulting posterior distributions allow us to determine whether the conditions are significantly different from one another by determining whether the highest density intervals (HDIs) of $b_{cond}$'s posterior distributions overlap or not. In our analyses, we use an HDI of 95\%.

>>>>

We fit the parameters to the data using a Bayesian approach \cite{kruschke_doing_2010}, using the STAN modeling software to perform the actual fit \cite{stan-software:2013}. In modeling the parameters, we use uninformative priors. The resulting posterior distributions allow us to determine whether the conditions are significantly different from one another by determining whether the highest density intervals (HDIs) of $b_{cond}$'s posterior distributions overlap or not. In our analyses, we use an HDI of 95\%.
